### 2015-04-06 cug_paper/02_design.tex
Fix figure 1 placement
Remove comment about figure 1 placement
Paper:  Add a footnote discussing the difference between pinned mem and pageable mem

\todo[inline]{We need to figure out how to force figure \ref{fig:communications} to display as page 2 or 3.  Right now, latex is putting it on the last page.}
\begin{figure*}[!t]
\centerline{
  \subfloat[Application sends write request message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide09}%
    \label{fig:comm_a}}
  \hfil
  \subfloat[Daemon allocates GPU memory and converts pointer into IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide10}%
    \label{fig:comm_b}}}
\centerline{
  \subfloat[Daemon sends reply message with IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide11}%
    \label{fig:comm_c}}
  \hfil
  \subfloat[Application writes data to GPU memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide12}%
    \label{fig:comm_d}}}    
\centerline{
  \subfloat[Application sends write complete message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide13}%
    \label{fig:comm_e}}
  \hfil
  \subfloat[Daemon copies data from GPU memory to system memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide14}%
    \label{fig:comm_f}}} 
\centerline{
  \subfloat[Daemon writes data to filesystem]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide15}%
    \label{fig:comm_g}}} 
\caption{Communications steps}
\label{fig:communications}
\end{figure*}

@@

Note that each write thread in the daemon has its own buffer in system memory.  Each of these buffers is deliberately kept fairly small - 16MB - in order to conserve resources.  Testing done on Titan shows that 16MB block sizes are large enough for \texttt{cudaMemcpy()} to give good performance.\cite{ac_guide}  Larger buffers would simply use up memory without improving performance noticeably. See Figure \ref{fig:transfer_bw}.

>>>>

\begin{figure*}[hp]
\centerline{
  \subfloat[Application sends write request message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide09}%
    \label{fig:comm_a}}
  \hfil
  \subfloat[Daemon allocates GPU memory and converts pointer into IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide10}%
    \label{fig:comm_b}}}
\centerline{
  \subfloat[Daemon sends reply message with IPC handle]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide11}%
    \label{fig:comm_c}}
  \hfil
  \subfloat[Application writes data to GPU memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide12}%
    \label{fig:comm_d}}}    
\centerline{
  \subfloat[Application sends write complete message to daemon]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide13}%
    \label{fig:comm_e}}
  \hfil
  \subfloat[Daemon copies data from GPU memory to system memory]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide14}%
    \label{fig:comm_f}}} 
\centerline{
  \subfloat[Daemon writes data to filesystem]{
    \includegraphics[width=2.5in]{figures/Data_Movement/Slide15}%
    \label{fig:comm_g}}} 
\caption{Communications steps}
\label{fig:communications}
\end{figure*}

@@

Note that each write thread in the daemon has its own buffer in system memory.  Each of these buffers is deliberately kept fairly small - 16MB - in order to conserve resources.  Testing done on Titan shows that 16MB block sizes are large enough for \texttt{cudaMemcpy()} to give good performance.\cite{ac_guide} Larger buffers would simply use up memory without improving performance noticeably. (See Figure \ref{fig:transfer_bw}.\footnote{Figure \ref{fig:transfer_bw} differentiates between 'pinned' memory and 'pageable' memory.  Pageable memory is allocated using regular \texttt{malloc()} or \texttt{new} calls.  Pinned memory is allocated using \texttt{cudaMallocHost()} or \texttt{cudaHostAlloc()}.\cite{cuda_pinned_memory}  This work uses pinned memory exclusively.})
